Sun v Shade leaves (WTCIII)

### 2015-03-20 markdown/shade.Rmd
finsihed bootstrapping lme of leaf phys
finished markdown of wtc data (1st draft)

---
## "Sun v Shade leaves (WTCIII)"
author: "Court Campany"
date: "March 17, 2015"
output: html_document
---
```{r knitr_options , include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=6,
echo=FALSE, message=FALSE,
fig.align='center', warning=FALSE)
```

```{r, results='asis', echo=FALSE}
library(knitr)
opts_knit$set(root.dir = '../')
```

@@

## Mesophyll Conducatnce

* We took leaf measurements at their current temperature (ambient, +3) in order to do paired comparisons across leaves at a large range of temperatures.  Im working on the paired comparisons now, but for this we will just focus on overall differences between leaf types.

* Further analysis is thus needed to tease apart any effects of temperature treatment as these are just the overall means over the 6 campaigns

* Here i seperated the well watered treatment from the drought treatment.  Im much more confident in the well watered trees as I was often on the border with drawdown and xsi for droughted leave. They do so similar patterns

```{r,results='asis'}
 source("functions and packages/functions.R")
 library(doBy)

   tablenames <- c( "Leaf Type", "Light", "Temperature","leaflight","Gm", "Gm(se)")
   names(gm_agg) <- tablenames

panderOptions("digits", 3)
pander(gm_agg,caption="Well Watered")

pander(gm_dr,caption="Drought")

* Next, Ill just show means of sun and shade leaf physiology and keep it simple by ignoring the temperature treatment. We can address that later.

###Photosynthesis vs Ci--------------------------------------------------------------------------------

#SUN leaves
Aci_sun_lm <- lm(Photo~ Ci, data=gm_c13,subset=leaflight=="sun-high")

  #predict
  #get apprpriate vector CC from sun leaves
  cidat <- gm_c13[gm_c13$leaflight=="sun-high", "Ci"]
  #generate sequence and then predict
  cisun_seq <- seq(min(cidat), max(cidat), length=101)
  cisun_pred <- predict.lm(Aci_sun_lm, newdata=data.frame(Ci=cisun_seq), interval="confidence")

  #get apprpriate vector CC from sun leaves
  cidat2 <- gm_c13[gm_c13$leaflight=="shade-low", "Ci"]
  #generate sequence and then predict
  cisha_seq <- seq(min(cidat2), max(cidat2), length=101)
  cisha_pred <- predict.lm(Aci_shade_lm, newdata=data.frame(Ci=cisha_seq), interval="confidence")

>>>>

---
title: "Sun v Shade leaves (WTCIII)"
author: "Court Campany"
date: "March 17, 2015"
output: html_document
---
```{r knitr_options , include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=6,
echo=FALSE, message=FALSE,
fig.align='center', warning=FALSE)
```

```{r, results='asis'}
library(knitr)
opts_knit$set(root.dir = '../')
```

### Mesophyll Conducatnce

* We took leaf measurements at their current temperature (ambient, +3) for paired comparisons across leaves at a large range of temperatures.

* For simplicity I have mostly generalized the results to sun vs shade leaves below.

* Further analysis is thus needed to tease apart any effects of temperature treatment as data below are overall means across the 6 campaigns

* Here i seperated the well watered treatment from the drought treatment.  Im much more confident in the well watered trees as I was often on the border with drawdown and xsi for droughted leave. They do so similar patterns but gm seems to be higher in droughted trees

```{r,results='asis'}
 source("functions and packages/functions.R")
 library(doBy)
library(pander)

   tablenames <- c( "Leaf Type", "Light", "Temperature","leaflight","Gm", "Gm(se)")
   names(gm_agg) <- tablenames
gm_agg2 <- gm_agg[c(3,4,5,6,1,2),]
row.names(gm_agg2) <- NULL

panderOptions("digits", 3)
pander(gm_agg2,caption="Well Watered")

  gm_dr2 <- gm_dr[c(3,4,5,6,1,2),]
  row.names(gm_dr2) <- NULL

pander(gm_dr2,caption="Drought")

* Here is a simple version of the paired comparisons.  Only shade low light and sun leaves are used (watered and drought treatments together).

```{r}
source("functions and packages/functions.R")
source("functions and packages/packages.R")
#source("scripts/read_data.R")
source("master_scripts/plot_objects_paired.R")

###there is no ch10 shade in march, check for this in script and paired comparisons

#read in gmsunsha
#gm data, no drought, no shade high
gm<- read.csv("calculated_data/gmes_wtc_pair.csv")
gm$variable <- as.factor(paste(gm$leaf, gm$temp, sep="-"))

gm2 <- gm[gm$leaflight != "shade-high",]

#paired id dfr
idDF <- data.frame(pair_id = unique(gm$pair_id))

gm_id <- summaryBy(gm~ variable+pair_id, data=gm2, FUN=c(mean), keep.names=TRUE)
gm_sp <- dlply(gm_id, .(variable), function(x) merge(x, idDF, all = TRUE))

par(cex.axis=1.21, cex.lab=1.51,las=1,mgp=c(3.5,1,0),mfrow=c(3,1),  
    omi=c(.5,0,0.1,0.1))   
# First Panel
par(mar=c(0,7,2,2))
plot(gm_sp[[4]][,3]~gm_sp[[3]][,3], pch=21, bg=wa[3], cex=2.5, ylab="", xlab="", xlim=c(0,.5), ylim=c(0,.5),
     axes=FALSE) 
abline(0,1, lty=2)
axis(1, labels=FALSE) 
axis(2, labels=TRUE) 
box()
legend(.4,.45, pairlab[1], pch=21, pt.bg=paircol[1], pt.cex=2,bg="white",inset = 0.06)

# Second panel   
par(mar=c(0,7,0,2))
plot(gm_sp[[1]][,3]~gm_sp[[3]][,3], pch=21, bg=wa[1], cex=2.5, ylab=gmlab, xlim=c(0,.5), ylim=c(0,.5),xlab="",
     axes=FALSE)     
abline(0,1, lty=2)
legend(.4,.45, pairlab[2], pch=21, pt.bg=paircol[2], pt.cex=2,bg="white",inset = 0.06)
axis(1, labels=FALSE) 
axis(2, labels=TRUE) 
box()

#third panel
par(mar=c(5,7,0,2))
plot(gm_sp[[2]][,3]~gm_sp[[3]][,3], pch=21, bg=wa[5], cex=2.5, ylab="", xlim=c(0,.5), ylim=c(0,.5),xlab=suatgm)   
abline(0,1, lty=2)
legend(.4,.45, pairlab[3], pch=21, pt.bg=paircol[3], pt.cex=2,bg="white",inset = 0.06) 
```

## Leaf Physiology
* Below are means of sun and shade leaf physiology, keeping it simple by ignoring the temperature treatment. We can address that later.

  title(ylab=satlab, mgp=ypos, cex=1.2)
  legend("topleft", leaflab2, pch=16,inset = 0.03, col=leafcol) 
```

```{r}  
source("functions and packages/functions.R")
source("master_scripts/plot_objects.R")
library(nlme)
library(doBy)

###Photosynthesis vs Ci
#library(nlme)
#SUN leaves
Aci_sun_lm <- lm(Photo~ Ci, data=gm_c13,subset=leaflight=="sun-high")

  #predict
  #get apprpriate vector CC from sun leaves
  cidat <- gm_c13[gm_c13$leaflight=="sun-high", "Ci"]
  #generate sequence and then predict
  cisun_seq <- seq(min(cidat), max(cidat), length=101)
  cisun_pred <- predict(Aci_sun_lm, newdata=data.frame(Ci=cisun_seq),interval="confidence")

  #get apprpriate vector CC from sun leaves
  cidat2 <- gm_c13[gm_c13$leaflight=="shade-low", "Ci"]
  #generate sequence and then predict
  cisha_seq <- seq(min(cidat2), max(cidat2), length=101)
  cisha_pred <- predict(Aci_shade_lm, newdata=data.frame(Ci=cisha_seq), interval="confidence")

@@
